### 2019-06-06 talk/animation/spaces11.tex
small (graphical) fixes to slides

\documentclass[tikz,border=3.14pt]{standalone}
\usepackage{../mymacros}
\usepackage{tikz-3dplot}
\begin{document}
\begin{tikzpicture}[]
\phantom{\draw[] (0,0,0) ellipse (2 and .75) node[right, shift={(1,1)}]{$\Theta$};}
\draw [fill, color=blue!60!white] (-0.7,-0.3,0) circle (1.5pt) node[above](a){$\vtheta_A$};
\draw [fill, color=red!60!white] (0.9,0.1,0) circle (1.5pt) node[above](b){$\vtheta_B$};
\phantom{
\draw[] (0,-3.5,0) ellipse (2.5 and .75) node[right, shift={(1,1)}]{$\mathcal{T}$};
\draw[fill, inner color=blue!60!white, outer color=white, draw=none, color=white] (-0.7,-3.5,0) ellipse (1.25 and .4) node[above, shift={(1,.2)}, color=blue!60!white]{$p_{\vtheta_A}$};
\draw[dashed, color=blue!60!white] (a) -- (-0.7,-3.5,0);
\draw[color=blue!60!white] (-0.7,-5,0) node (c) {$J(\vtheta_A)$};
\draw[->, dashed, color=blue!60!white] (-0.7,-3.5,0) -- (c);
}
\draw[color=blue!60!white] (-0.7,-5,0) node (c) {$J(\vtheta_A)$};
\draw[->, dashed, color=blue!60!white] (a) -- (c);
\draw[color=red!60!white] (0.9,-5,0) node (d) {$J(\vtheta_B)$};
\draw[->, dashed, color=red!60!white] (b) -- (d);
\draw[fill=black] (-1.5,-1.5,0) rectangle (1.7,-3.5,0) node[pos=.5, color=white]{\bf\Large MAB};
\end{tikzpicture}
\end{document}

>>>>

\documentclass[tikz,border=3.14pt]{standalone}
\usepackage{../mymacros}
\usepackage{tikz-3dplot}

\definecolor{poliblue1}{RGB}{93,138,168} 
\definecolor{poliblue2}{RGB}{41,76,113}
\definecolor{poliblue3}{RGB}{25,43,67}
\definecolor{orangep}{RGB}{251,146,116}
\definecolor{redp}{RGB}{245,86,91}
\definecolor{greenp}{RGB}{73,165,150}

\begin{document}
\begin{tikzpicture}[]
\phantom{\draw[] (0,0,0) ellipse (2 and .75) node[right, shift={(1,1)}]{$\Theta$};}
\draw [fill, color=poliblue1] (-0.7,-0.3,0) circle (1.5pt) node[above](a){$\vtheta_A$};
\draw [fill, color=redp] (0.9,0.1,0) circle (1.5pt) node[above](b){$\vtheta_B$};
\phantom{
\draw[] (0,-3.5,0) ellipse (2.5 and .75) node[right, shift={(1,1)}]{$\mathcal{T}$};
\draw[fill, inner color=poliblue1, outer color=white, draw=none, color=white] (-0.7,-3.5,0) ellipse (1.25 and .4) node[above, shift={(1,.2)}, color=poliblue1]{$p_{\vtheta_A}$};
\draw[dashed, color=poliblue1] (a) -- (-0.7,-3.5,0);
\draw[color=poliblue1] (-0.7,-5,0) node (c) {$J(\vtheta_A)$};
\draw[->, dashed, color=poliblue1] (-0.7,-3.5,0) -- (c);
}
\draw[color=poliblue1] (-0.7,-5,0) node (c) {$J(\vtheta_A)$};
\draw[->, dashed, color=poliblue1] (a) -- (c);
\draw[color=redp] (0.9,-5,0) node (d) {$J(\vtheta_B)$};
\draw[->, dashed, color=redp] (b) -- (d);
\draw[fill=black] (-1.5,-1.5,0) rectangle (1.7,-3.5,0) node[pos=.5, color=white]{\bf\Large MAB};
\end{tikzpicture}
\end{document}

### 2019-06-06 talk/animation/spaces4.tex
small (graphical) fixes to slides

\documentclass[tikz,border=3.14pt]{standalone}
\usepackage{../mymacros}
\usepackage{tikz-3dplot}
\begin{document}
\begin{tikzpicture}[]
\draw[] (0,0,0) ellipse (2 and .75) node[right, shift={(1,1)}]{$\Theta$};
\draw [fill, color=blue!60!white] (-0.7,-0.3,0) circle (1.5pt) node[above](a){$\vtheta$};
\draw[] (0,-3.5,0) ellipse (2.5 and .75) node[right, shift={(1,1)}]{$\mathcal{T}$};
\draw[fill, inner color=blue!60!white, outer color=white, draw=none, color=white] (-0.7,-3.5,0) ellipse (1.25 and .4) node[above, shift={(1,.2)}, color=blue!60!white]{$p_{\vtheta}$};
\draw[dashed, color=blue!60!white] (a) -- (-0.7,-3.5,0);
\phantom{
\draw [fill, color=black] (-1.1,-3.6,0) circle (1.5pt) node[above](b){$\tau$};
\draw[] (-1.1,-5,0) node (c) {$R(\tau)$};
\draw[->] (b) -- (c);
}
\end{tikzpicture}
\end{document}

>>>>

\documentclass[tikz,border=3.14pt]{standalone}
\usepackage{../mymacros}
\usepackage{tikz-3dplot}
\usetikzlibrary{fadings}

\definecolor{poliblue1}{RGB}{93,138,168} 
\definecolor{poliblue2}{RGB}{41,76,113}
\definecolor{poliblue3}{RGB}{25,43,67}
\definecolor{orangep}{RGB}{251,146,116}

\begin{document}
\begin{tikzpicture}[]
\draw[dashed, color=poliblue1, opacity=0.3] (-0.7,-0.3,0) -- (-1.93,-3.5,0);
\draw[dashed, color=poliblue1, opacity=0.3] (-0.7,-0.3,0) -- (0.5,-3.5,0);
\draw[] (0,0,0) ellipse (2 and .75) node[right, shift={(1,1)}]{$\Theta$};
\draw [fill, color=poliblue1] (-0.7,-0.3,0) circle (1.5pt) node[above](a){$\vtheta$};
\draw[] (0,-3.5,0) ellipse (2.5 and .75) node[right, shift={(1,1)}]{$\mathcal{T}$};
\draw[fill, inner color=poliblue1, outer color=white, draw=none, color=white] (-0.7,-3.5,0) ellipse (1.25 and .4) node[above, shift={(.5,.25)}, color=poliblue1]{$p_{\vtheta}$};
%\draw[dashed, color=poliblue1] (a) -- (-0.7,-3.5,0);
\draw [fill, color=black] (-1.1,-3.6,0) circle (1.5pt) node[above](b){$\tau$};
\draw[] (-1.1,-5,0) node (c) {$R(\tau)$};
\draw[->] (b) -- (c);
\phantom{\draw[color=poliblue1] (-0.7,-5,0) node (c) {$J(\vtheta)$};}
\end{tikzpicture}
\end{document}

### 2019-06-06 talk/animation/spaces8.tex
small (graphical) fixes to slides

\begin{document}
\begin{tikzpicture}[]
\draw[] (0,-3.5,0) ellipse (2.5 and .75) node[right, shift={(1,1)}]{$\mathcal{T}$};
\draw[fill, inner color=blue!60!white, outer color=white, draw=none, color=white] (-0.7,-3.5,0) ellipse (0.5 and .2) node[above, shift={(-.1,.1)}, color=blue!60!white]{$p_{\vtheta_1}$};

\draw[fill,color=red!60!white, path fading = fade out, draw=none] (-0.5,-3.7,0) ellipse (0.5 and .2);
\draw[color=red!60!white] (-0.8,-3.8,0) node{$p_{\vtheta_2}$};

\draw[fill,color=green!60!white, path fading = fade out, draw=none] (-0.2,-3.5,0) ellipse (0.5 and .2);
\draw[color=green!60!white] (0.1,-3.2,0) node{$p_{\vtheta_{t-1}}$};

\draw[fill,color=black!60!white, path fading = fade out, draw=none] (1.,-3.7,0) ellipse (1 and .3);
\draw[color=black!60!white] (1.2,-3.4,0) node{$p_{\vtheta}$};

>>>>

\definecolor{poliblue1}{RGB}{93,138,168} 
\definecolor{poliblue2}{RGB}{41,76,113}
\definecolor{poliblue3}{RGB}{25,43,67}
\definecolor{orangep}{RGB}{251,146,116}
\definecolor{redp}{RGB}{245,86,91}
\definecolor{greenp}{RGB}{73,165,150}
\definecolor{waterp}{RGB}{134,195,180}

\begin{document}
\begin{tikzpicture}[]
\draw[] (0,-3.5,0) ellipse (2.5 and .75) node[right, shift={(1.5,1)}]{$\mathcal{T}$};
\draw[fill, inner color=poliblue1, outer color=white, draw=none, color=white] (-0.7,-3.5,0) ellipse (0.5 and .2) node[above, shift={(-.1,.1)}, color=poliblue1]{$p_{\vtheta_1}$};

\draw[fill,color=redp, path fading = fade out, draw=none] (-0.5,-3.7,0) ellipse (0.5 and .2);
\draw[color=redp] (-0.8,-3.8,0) node{$p_{\vtheta_2}$};

\draw[fill,color=orangep, path fading = fade out, draw=none] (-0.2,-3.5,0) ellipse (0.5 and .2);
\draw[color=orangep] (0.1,-3.2,0) node{$p_{\vtheta_{t-1}}$};

\draw[fill,color=waterp!80!black, path fading = fade out, draw=none] (1.,-3.7,0) ellipse (1 and .3);
\draw[waterp!80!black] (1.2,-3.4,0) node{$p_{\vtheta}$};

\draw[line width = 1.5pt, color=greenp,-latex] (-0.4,-3.2,0) arc[start angle=180,end angle=0, x radius = 0.8 cm , y radius =1 cm] node[shift={(-0.75,1.2)}]{\bf MIS};

### 2019-06-06 talk/animation/spaces9.tex
updated slides; poster skeleton
small (graphical) fixes to slides

\begin{document}
\begin{tikzpicture}[]
\draw[] (0,-3.5,0) ellipse (2.5 and .75) node[right, shift={(1,1)}]{$\mathcal{T}$};
\draw[fill,color=violet!60!white, path fading = fade out, draw=none] (-0.5,-3.5,0) ellipse (.8 and .4);
\draw[color=violet!60!white] (-0.9,-3.2,0) node{$\Phi_t$};

\draw[fill,color=black!60!white, path fading = fade out, draw=none] (1.,-3.7,0) ellipse (1 and .3);
\draw[color=black!60!white] (1.2,-3.4,0) node{$p_{\vtheta}$};

>>>>

\definecolor{poliblue1}{RGB}{93,138,168} 
\definecolor{poliblue2}{RGB}{41,76,113}
\definecolor{poliblue3}{RGB}{25,43,67}
\definecolor{orangep}{RGB}{251,146,116}
\definecolor{redp}{RGB}{245,86,91}
\definecolor{greenp}{RGB}{73,165,150}
\definecolor{violetp}{RGB}{215,113,161}
\definecolor{waterp}{RGB}{134,195,180}

\begin{document}
\begin{tikzpicture}[]
\draw[] (0,-3.5,0) ellipse (2.5 and .75) node[right, shift={(1.5,1)}]{$\mathcal{T}$};
\draw[fill,color=violetp, path fading = fade out, draw=none] (-0.5,-3.5,0) ellipse (.8 and .4);
\draw[color=violetp] (-0.9,-3.2,0) node{$\Phi_t$};

\draw[fill,color=waterp!80!black, path fading = fade out, draw=none] (1.,-3.7,0) ellipse (1 and .3);
\draw[color=waterp!80!black] (1.2,-3.4,0) node{$p_{\vtheta}$};

\draw[line width = 1.5pt, color=orangep,latex-latex] (-0.5,-3.5,0) --  (1.,-3.7,0) node[shift={(-0.75,0.5)}]{$d_2$};
